Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-17 papers/B1555_EdgeOn/B1555_letter.tex
add some references

\section{Introduction}
To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999}. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group. Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way. Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, the number of flux ratio anomalous systems (numbers?) in radio bands is not large enough to provide unbiased statistics. Another approach using narrow-line specstroscopy \citep{N14} may be able to find out more flux ratio anomalous strong lensing systems. All of these results show the power of lensing effects in substracture studies.\\
On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

>>>>

\section{Introduction}
	To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in local universe. Most satellite galaxies are too faint to be directly detected. Futhermore, low-mass dark matter subhaloes may contain too less gas to form stats \citep{P11}. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis. All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.
